Malacology: A Programmable Storage System Built on Ceph

### 2016-05-08 paper/paper.tex
Adds preamble to latex file

\usepackage{times}
\usepackage{fullpage}

\begin{document}

\title{Malacology: A Programmable Storage System Built on Ceph}
\author{Paper \# 123}
\date{}
\maketitle
\thispagestyle{empty}

@@

So called ``bolt-on'' services are 3rd party systems that are integrated
into the system to provide functionality and improve performance for
common use-cases (e.g.~a metadata service). In addition to sacrificing
simplicity, ``bolt-on'' services often duplicate functionality and
execute redundant code, unnecessarily increasing the likelihood of bugs
or worse, introducing unpredictable performance problems. For example,
we are developing a distributed shared-commit log on Ceph called ZLog.
ZLog uses a ``sequencer'' to distribute tokens to clients that want to
append to the end of the log. When designing the sequencer, we
considered bolting on Zookeeper \cite{} as a service. Zookeeper would
satisfy our requirements by proiding a network and transaction stack but
it would perform poorly because Zookeeper persists its data and the
sequencer can be in-memory and volatile. A Zookeeper sequencer would
adhere to the pre-conceived notions of storage, namely that data in
storage systems should be safe from data loss, but would introduce
unecessary scalability limits \cite{Neha HDFS namenode example}.

@@

This effectively decouples policy from mechanism, which helps future
designers explore trade-offs and isolates policy development from
code-hardened systems. Decoupling policy mechanism is not a new
technique but designing the storage system with programmability as a
first-class citizen is credits policy/mechanism separation as the
biggest reason for the success of the block allocation mechanisms in the
Fast File System\textasciitilde{}\cite{mckusick:fast2015-FFS} yet there
are no mechanisms for transparently exposing and modifying the
underlying logic in modern file systems.

@@

\section{Bibliography}\label{bibliography}

>>>>

\usepackage{times}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{biblatex}
\bibliography{refs}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Malacology: A Programmable Storage System Built on Ceph},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

\title{Malacology: A Programmable Storage System Built on Ceph}
\author{Paper \# 123}
\date{}
\begin{document}

\maketitle

@@

So called ``bolt-on'' services are 3rd party systems that are integrated
into the system to provide functionality and improve performance for
common use-cases (e.g.~a metadata service). In addition to sacrificing
simplicity, ``bolt-on'' services often duplicate functionality and
execute redundant code, unnecessarily increasing the likelihood of bugs
or worse, introducing unpredictable performance problems. For example,
we are developing a distributed shared-commit log on Ceph called ZLog.
ZLog uses a ``sequencer'' to distribute tokens to clients that want to
append to the end of the log. When designing the sequencer, we
considered bolting on Zookeeper \autocite{} as a service. Zookeeper would
satisfy our requirements by proiding a network and transaction stack but
it would perform poorly because Zookeeper persists its data and the
sequencer can be in-memory and volatile. A Zookeeper sequencer would
adhere to the pre-conceived notions of storage, namely that data in
storage systems should be safe from data loss, but would introduce
unecessary scalability limits \autocite{Neha HDFS namenode example}.

@@

This effectively decouples policy from mechanism, which helps future
designers explore trade-offs and isolates policy development from
code-hardened systems. Decoupling policy mechanism is not a new
technique but designing the storage system with programmability as a
first-class citizen is credits policy/mechanism separation as the
biggest reason for the success of the block allocation mechanisms in the
Fast File System\textasciitilde{}\autocite{mckusick:fast2015-FFS} yet there
are no mechanisms for transparently exposing and modifying the
underlying logic in modern file systems.

@@

\printbibliography
